\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-08 coqimpl.tex
related work on EP
excuse

The implementation works by translating programs in \Lang syntax into
programs that can be checked and evaluated by Coq.
The translation is compatible with interactive theorem proving, in that
a family is translated piece by piece, allowing each field to be defined
and checked separately.
The translation is modular and efficient, in that
code inherited from a base family need not be retranslated or rechecked.

@@

Upon the conclusion of a family definition (e.g., \lsti{End}~\lsti{STLCFix}),
\lsti{self} parameters in the translations of the fields must be instantiated,
so that references like \lsti{STLCFix.typesafe} can be translated.
This is done by assembling the \lsti{self}-parameterized pieces into a single module.
%
For example, module \lsti{STLC} in \cref{fig:stlc-compiled} is generated
upon \lsti{End}~\lsti{STLCFix}.
All the fields are added to this module in the same order as they appear in the family definition.

@@

>>>>

The implementation works by translating programs in \Lang syntax into
programs that can be checked and evaluated by Coq.
The translation is compatible with interactive theorem proving, in that
a family is translated piece by piece, allowing each field to be defined
and checked separately.
The translation is modular and efficient, in that
code compiled for non-further-bindable fields of a base family
is shared with derived families without having to be rechecked.

@@

Upon the conclusion of a family definition (e.g., \lsti{End}~\lsti{STLCFix}),
\lsti{self} parameters in the translations of the fields must be instantiated,
so that references like \lsti{STLCFix.typesafe} can be translated.
This is done by assembling the \lsti{self}-parameterized pieces into a single module.
%
For example, module \lsti{STLC} in \cref{fig:stlc-compiled} is generated
upon \lsti{End}~\lsti{STLC}.
All the fields are added to this module in the same order as they appear in the family definition.

@@

One may argue that because the first four constructors of \lsti{tm} are
repeated in \lsti{STLCFix}, the translation does not satisfy the
modular compilation requirement. Compared with alternatives that create
wrapper inductive types, we consider it a small price to pay in return
for the clarity of implementation especially given that compiled case handlers
are entirely reusable without rechecking.
